Impact of grids and dynamical cores in CESM2.2 on the surface mass balance of the Greenland Ice Sheet

### 2022-03-22 arcticgrids.tex
new basin plot

@@

\begin{figure}[t]
\begin{center}
         \includegraphics[width=100mm]{figs/temp_transect_obsperiod.pdf}
\end{center}
\caption{.}
\label{fig:trans}
\end{figure}

\begin{figure}[t]
\begin{center}
\begin{tabular}{cccc}
         \includegraphics[width=100mm]{figs/temp_ktransect.pdf} \\
         \includegraphics[width=100mm]{figs/temp_btransect.pdf} \\
\end{tabular}
\end{center}
\caption{.}
\label{fig:ztrans}
\end{figure}

>>>>

\begin{figure}[t]
\begin{center}
         \includegraphics[width=100mm]{figs/temp_tseries_BASIN.pdf}
\end{center}
\caption{.}
\label{fig:basin}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
         \includegraphics[width=130mm]{figs/temp_transect_obsperiod.pdf}
\end{center}
\caption{.}
\label{fig:trans}
\end{figure}

\begin{figure}[t]
\begin{center}
\begin{tabular}{cccc}
         \includegraphics[width=130mm]{figs/temp_ktransect.pdf} \\
         \includegraphics[width=130mm]{figs/temp_btransect.pdf} \\
\end{tabular}
\end{center}
\caption{.}
\label{fig:ztrans}
\end{figure}
